dendro

### 2017-04-10 analysis/test-bai.Rmd
update piovesan test bai

---
title: "dendro"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
---

```{r, warning=FALSE, message=FALSE}}
library("tidyverse")
library("dplR")
```

@@

# sj 
sj <- read.rwl(fname=paste0(di, '/data/SNA_sanjuan.rwl'), format="tucson")
```

@@

@@

@@

```{r}
# BAI dplR
baisj <- bai.out(rwl = sj, diam = diam_cores)

```{r}

# Function to compute BAI

# rwl_file
myrwl <- sj

@@

@@

@@

    for (i in seq_len(ncol(rwl))) {
        dat <- rwl[[i]]
        dat2 <- na.omit(dat)
        if (is.null(diam)) 
            d <- sum(dat2) * 2
        else d <- diam.vec[i]
        r0 <- d/2 - c(0, cumsum(rev(dat2)))
        bai <- -pi * rev(diff(r0 * r0))
        na <- attributes(dat2)$na.action
        no.na <- n.vec[!n.vec %in% na]
        out[no.na, i] <- bai
    }
    out

bai <- (pi/4)*(dbh^2 - ((d - 2*w)^2))

sjD <- sj[["SNA0101"]]
dbh <- 1170 / pi

baiD <- bai.out(sj[["SNA0101"]], dbh)

rwl

# Test bai.out 
s1 <- sj[1]
b1 <- bai.out(s1)/100

>>>>

---
title: "dendro"
author: "AJ Perez-Luque (@ajpelu)"
date: "2017 Feb"
output:  
  md_document:
    variant: markdown_github
bibliography: references.bib 
csl: ecology.csl
---

```{r, warning=FALSE, message=FALSE}
library("tidyverse")
library("dplR")
```

@@

# sj 
sj <- read.rwl(fname=paste0(di, '/data/SNA_sanjuan.rwl'), format="tucson")
sjt <- read.rwl(fname=paste0(di, '/data/sj_test.rwl'), format="tucson")
```

@@

Lectura y preparación de datos de diámetro

@@

# remove diamm of cores without bark 
diam_cores_sj <- diam_cores %>% filter(! id_cores %in% id_cores_no_bark)
```

## Cómputo del BAI

He construido una funcion para el computo del BAI, teniendo en cuenta la aproximación de [@Piovesan2008]

```{r} 
## BAI Function Piovesan

i <- "SNA0101"

bai_piovesan <- function(rwdf, diam_df){
  # rwdf: a ringwidth dataframe. row: years; col: id_cores
  # diam_df: a dataframe with diameter and id_core (two columns)

  # Output 
  bai <- rwdf

  # length years in Ring-width Data frame 
  vec_ly <- seq_len(nrow(rwdf))

  # ID cores 
  cores <- colnames(rwdf)

  for (i in cores){ 
    # 1 # Select core 
    id_core <- i

    # 2 # Select serie 
    rs <- rwdf[[id_core]]

    # 3 # Select diameter 
    dbh <- subset(diam_df, id_cores == id_core)
    dbh <- dbh[,2]

    # 4 # Prepare data to compute bai 
    #### Omit NA 
    rsomit <- na.omit(rs)

    #### Revert w 
    rs_rev <- rev(rsomit)

    # Cumsum rever w
    # cum_rs_rev <- cumsum(rs_rev)
    cum_rs_rev <- c(0, cumsum(rs_rev))

    # Compute d_{t} 
    d <- dbh - 2*cum_rs_rev

    # Remove last element 
    d <- d[-length(d)]

    # Bai
    b <- rev((pi/4) * ((d)^2 - (d - 2*rs_rev)^2))

    # Store BAI and NA 
    ### Which elements are NA? 
    na <- attributes(rsomit)$na.action
    ### Which ones no? 
    no_na <- vec_ly[!vec_ly %in% na]
    ### Put bai in those element with no NA
    bai[no_na, i] <- b 
  }
  bai 
}

# Test 
b_test_piovesan <- bai_piovesan(rwdf = sj_cor, diam_df = diam_cores_sj)
b_test_dplR <- bai.out(rwl = sj_cor, diam = diam_cores_sj)

@@

```{r, eval=FALSE, echo=FALSE}
# BAI dplR
baisj <- bai.out(rwl = sj_cor, diam = diam_cores_sj)

baisjt <- bai.out(rwl = sjt)

# Function to compute BAI (Piovesan et al)

# rwl_file
myrwl <- sj_cor
# Diameter df  
diam_df <- diam_cores_sj

# Core
id_core <- 'SNA0101'

# Ring-width serie
myrwl_serie <- myrwl[[id_core]]

# Diameter for core id_core 
dbh <- subset(diam_df, id_cores == id_core)
dbh <- dbh[,2]

myrwl_serie2 <- na.omit(myrwl_serie)
cum

r0 <- dbh/2 - c(0,cumsum(rev(myrwl_serie2)))

bai <- (pi/4)*(dbh^2 - ((dbh - 2*myrwl_serie)^2))

s <- myrwl_serie[94:96]

d <- sum(s)*2

rev(s)

@@

diam_df_i <- diam_cores_sj[1]

@@

bai <- 
diam.vec <- diam[, 2]

########## test Piovesan
# rwl_file
myrwl <- baisj

#id_core

dbh <- 372.4226

@@
